Practice Problems

### 2023-10-12 Lahman Analysis/Rough Analysis/BinomialRoughAnalysis.qmd
Finished through medium practice problems

Batting %>% 
  filter(yearID >= 1945)
```

@@

>>>>

Batting <- Batting %>% 
  filter(yearID >= 1945) %>% 
  select(playerID, yearID, lgID, AB, AB, HR) %>% 
  mutate(lg = ifelse(lgID=="NL",1,2))
```

@@

```{r}
head(Batting)
```

```{r}
slim <- list(
  AB = Batting$AB,
  HR = Batting$HR,
  LG = Batting$lg
)

str(slim)
```

```{r}
u1 <- ulam(
  alist(
    HR ~ binomial(p),
    logit(p) = ,
  ), data=slim, chains=4, cores=4
)
```

### 2023-10-12 Stats Rethinking/Ch11/Practice Problems.qmd
Finished most easy problems
Finished through medium practice problems

@@

@@

@@

@@

# 11M2

@@

# 11M3

Explain why the logit ink is appropriate for a binomial generalized linear model.

# 11M4

@@

@@

@@

Use `quap` to construct a quadratic approximate posterior distribution for the chimpanzee model that includes a unique intercept for each actor `m11.4`. Compare the quadratic approximation to the posterior distribution produced instead from MCMC/ Can you explain both the differences and the similarities between the approximate and the MCMC distributions? Relax the prior on the actor intercepts to Normal(0,10). Re-estimate the posterior using both `ulam` and `quap`. Do the differences increase or decrease? Why?

# 11M8

@@

@@

# 11H6

>>>>

```{r}
logit(.35)
```

@@

```{r}
inv_logit(3.2)
```

@@

```{r}
inv_logit(1.7)
```

A one unit change in the independent variable results in a 0.85 change in the dependent variable.

@@

Having an offset allows us to analyze the same count variable over different time frames. An example of this in the chapter was when the original monastery was doing so well that the author was considering buying a second one. Both produced books but the original monastery tracked by day while the second tracked by week. Thus, using the offset factor $\tau$, we can compare the two monasteries as if they were recorded at the same rate.

@@

Aggregated data will have a larger probability simply because it contains an extra factor in the log-probabilities not present for disaggregated data (339).

# 11M2\*

@@

He never explicitly states coefficient interpretation in 11.2.

# 11M3\*

Explain why the logit link is appropriate for a binomial generalized linear model.

Logistic regression makes sense for binomial since in a logistic regression you can only have either a 0 or 1 for the final outcome. Thus modeling a binomial will follow this 0 or 1 trend.

# 11M4\*

@@

Possibly because a logarithmic function implies that the growth of the model parameter, this case $\lambda$ (346), will grow exponentially.

@@

When priors are flat, then both distributions have flat priors

@@

Use `quap` to construct a quadratic approximate posterior distribution for the chimpanzee model that includes a unique intercept for each actor `m11.4`. Compare the quadratic approximation to the posterior distribution produced instead from MCMC. Can you explain both the differences and the similarities between the approximate and the MCMC distributions? Relax the prior on the actor intercepts to Normal(0,10). Re-estimate the posterior using both `ulam` and `quap`. Do the differences increase or decrease? Why?

## Prepare m11.4

```{r}
data(chimpanzees)
d <- chimpanzees
d$treatment <- 1+d$prosoc_left + 2*d$condition
```

```{r}
dat_list <- list(
  pulled_left = d$pulled_left,
  actor = d$actor,
  treatment = as.integer(d$treatment)
)
```

```{r}
m11.4 <- ulam(
  alist(
    pulled_left ~ dbinom(1,p),
    logit(p) <- a[actor] + b[treatment],
    a[actor] ~ dnorm(0,1.5),
    b[treatment] ~ dnorm(0,0.5)
  ), data=dat_list, chains=4, cores=4, log_lik = TRUE
)
```

```{r}
precis(m11.4, depth=2)
```

## Part 1

```{r}
m11.4.2 <- quap(
  alist(
    pulled_left ~ dbinom(1,p),
    logit(p) <- a[actor] + b[treatment],
    a[actor] ~ dnorm(0,1.5),
    b[treatment] ~ dnorm(0,0.5)
  ), data=dat_list
)
```

```{r}
precis(m11.4.2, depth=2)
```

In general, it appears that the coefficients of "a" generally became lower while the coefficients for "b" became higher.

## Part 2

```{r}
m11.4.3 <- ulam(
  alist(
    pulled_left ~ dbinom(1,p),
    logit(p) <- a[actor] + b[treatment],
    a[actor] ~ dnorm(0,10),
    b[treatment] ~ dnorm(0,0.5)
  ), data=dat_list, chains=4, cores=4, log_lik = TRUE
)
```

```{r}
precis(m11.4.3, depth=2)
```

```{r}
m11.4.4 <- quap(
  alist(
    pulled_left ~ dbinom(1,p),
    logit(p) <- a[actor] + b[treatment],
    a[actor] ~ dnorm(0,10),
    b[treatment] ~ dnorm(0,0.5)
  ), data=dat_list
)
```

```{r}
precis(m11.4.4, depth=2)
```

This greatly exaggerated the differences seen between the models. However, it seems to affect `quap` more than it did for `ulam`.

@@

```{r}
#Creat m11.3

m11.3 <- quap(
  alist(
    pulled_left ~ dbinom(1,p),
    logit(p) <- a + b[treatment],
    a ~ dnorm(0,1.5),
    b[treatment] ~ dnorm(0,0.5)
  ), data=dat_list
)
```

```{r}
compare(m11.4, m11.3, func=WAIC)
```

Obviously, the MCMC model does much better than the `quap` models.

@@
